---
title: "Pitch - nLargestCities"
author: "Mathieu MICHEL"
date: "26/08/2020"
output: 
   ioslides_presentation: 
   widescreen: true
   incremental: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(xlsx)
library(tidyverse)
library(knitr)
```

## The idea

- Have you ever been curious about the most populous cities in the world?

> - **who are they?**

> - <div class="red">**where even are they?**</div> 


## Now there is a free way to find out!!

nLargestCities allows you to scroll through the number of largest cities of your choice (but limited to the top 50).

The app reactivly showcases the cities' population in a bar plot, 
and provide a summary statistics per continent.

With trusted content from Wikipedia: https://en.wikipedia.org/wiki/List_of_largest_cities

## Teasing with n=5

```{r plot, fig.height=1.5, echo = FALSE}

data <- read.xlsx("Largest Cities.xlsx", sheetIndex = 1)

data$city <- factor(data$city, levels = data$city)

ggplot(data=data[1:5,], aes(x=city, y=population, fill=continent)) +
       geom_bar(stat="identity") + coord_flip() 

###

table <- aggregate(data[1:5,]$city, 
                           by=list(data[1:5,]$continent),
                           FUN='length')
        
        table2 <- aggregate(data[1:5,]$pop, 
                            by=list(data[1:5,]$continent),
                            FUN='mean')
        table2$x <- round(table2$x/1000000,3)
        
        table3 <- cbind(table,table2$x)
        
        names(table3) <- c("Continent",
                           "Number of cities in the Top-5",
                           "Average population in biggest cities (millions)")
        
        kable(table3)

```


# Thank you for reading!

Eager to learn more about cities 6 to 50?

Go to:


[**nLargestCities**](https://mathieu-michel.shinyapps.io/DevDataProd_Project/)



And let's make the world a better place by knowing more about big cities!

